Do Drivers Dream of Walking? An Investigation of Travel Mode Dissonance from the Perspective of Affective Values

### 2020-08-17 Dissonance_Santiago_v2/Dissonance_Santiago_v2.Rmd
v2 Revisions with BML

The literature on SWB has demonstrated a relationship between people’s perceptions and satisfaction with their daily travel [e.g., @Smith2017commute; @Stlouis2014happy; @Mokhtarian2018travel]. Scholars have shown that accessibility is among the most studied factors that influences subjective wellbeing [@Delbosc2012role], and activities have a direct impact on travel satisfaction [@Bergstad2011subjective]. Delbosc [-@Delbosc2012role, p. 28], for instance, has summarized the most significant influences on psychological wellbeing: poverty and employment, meaningful relationships and health. However, understanding the components that affect these perceptions implies the differentiation between affective (also named as symbolic-affective) and instrumental values [@Bergstad2011affective]. Steg et al. (2011) have compared symbolic-affective and instrumental-reasoned motives for car-use, and similar findings are reported in other studies [e.g., @Gatersleben2007affective; @Lois2009relationship]. Previous research also demonstrates how socio-demographic factors affect the levels of SWB, includin income [@Clark1996satisfaction; @Ferrer2005income], education and unemployment [@Argyle1999causes], age [@Diener1997subjective], and gender [@Tesch2008gender]. However, further research beyond the determinants of trip satisfaction is needed to understand how these socio-demographic variables connect with the affective reactions to various modes of travel [@Stlouis2014happy].

@@

The case study for the present research is Santiago. Santiago is the capital of Chile, a country with one of the highest levels of socio-economic inequality in the world. A tangible manifestation of the inequalities experienced by many in Chile is the large disparity in the relative cost of transportation, travel time, and distance traveled by different socio-economic segments of the population. To further complicate matters, strong spatial segregation also conditions car ownership and the use of public transportation – the higher the income, the higher the use of the automobile; conversely, the lower the income, the higher the reliance on public transportation. Although the transportation experience is but one of many dimensions of inequality, the experiences in this sector have triggered exceptional discomfort and dissatisfaction among the public. Recent social unrest, triggered by a seemingly minor hike in the fare of public transportation, has brought many of these concerns to the forefront of the public conscience in dramatic fashion [e.g., @Davis2019; @GuardiolaRivera2019; @Sehnbruch2019].

@@

The study is based on a survey conducted in the city of Santiago during the months of November and December of 2016, at the end of the Spring and beginning of Summer seasons. The survey collected information on a wide range of transportation and related issues, and the data collection protocol considered a quota-sampling method for gathering the information, considering the socio-demographic information from Pre-Census of 2012. The survey was carried out face-to-face in centers of activity with dense provision of offices, services, and educational centers. An equal representation of both genders and a representation of the proportion of inhabitants per area were chosen as relevant characteristics of the sample. In total, there were $n=451$ valid reponses, although not every response was complete and some questions have missing values.

The study considers data from 3 out of 8 sections of a longer survey. The relevant sections of the survey concern the individual characteristics of respondents, their feelings and affective responses related to their commute, and aspects describing their regular commute trips. In terms of individual characteristics and their commute, participants were asked socio-demographic information, including age (coded in three classes: younger than 35, older than 35 but younger than 55, and 55 and olde); level of education (three classes: Kindergarden to grade 12, or K-12, technical diploma or university graduate, and graduate degree), income (three classes, by tertile), and the typical duration of the respondent's regular commute (four classes, by duration in minutes). The descriptive statistics of the sample appear in Figure \ref{fig:descriptive-statistics}. The sample trends to younger (56% is younger than 34 years old) and well-educated respondents (68% of respondents having technical or professional education), with an almost uniform distribution of income levels. The trend in typical commute time is towards longer commutes – e.g. 55% of the trips are longer than 40 minutes, and from those 56% corresponds to trips over the 60 minutes long.

@@

The next individual attribute that we examine is income, and in this case we detect significant differences in dissonance for three affective values: Poverty, Luxury, and Status. Since Poverty is a negative affect, we see here that lower income individuals tend to associate this feeling to their primary mode of commuting with higher frequency (almost 20% of the time) than other income groups. Whereas approximately 16% of mid-income people are dissatisfied with their primary mode of travel when it comes to evoking feelings of Poverty, less than 7% of high income individuals are. Dissonance with respect to Luxury and Status also tends to be more common among lower income individuals, and declines substantially for mid- and high income respondents. Notice as well that the frequency of dissonance is higher in terms of Luxury than Status for mid- and high income people.

@@

The preceding analysis indicates that there is significant mode dissonance along various dimensions and for various affective values. This is for the most part in line with previous research, although by examining different affective values individually instead of a summary measure of wellbeing, we are able to differentiate better the affective reactions of travelers. Less is known about the values that travelers associate with modes _other_ than the one they use. For this reason, after developing a profile of the travelers who experience mode dissonance in the preceding section, we are now interested in the responses of travelers with respect to the modes they ideally tend to associate with various affective values. 
For this analysis we employ a visualization technique known as _faceting_. Bar charts are used to plot the proportions of respondents who associate each mode of transportation with an affective value. Faceting allows us to explore these proportions in a multivariate way by slicing the data according to additional attributes. The result is a visual representation of a multi-way contingency table. Please note that due to the small numbers of travellers who use modes categorized as "Other" we henceforth exclude them from the analysis.

@@

Active travelers rarely experience dissonance with respect to Freedom, Enjoyment, and Happiness. And although the experience of dissonance is more frequent with respect to Luxury and Status, there is still a sizeable plurality of active travellers who associate these two affective values with active travel, _not_ the car (contrast these to the responses of public transit users.)

@@

With respect to luxury and status, we see again that these two values generally are attributed to the car, but with some interesting differences by income and primary mode of travel. Indeed, higher income active travelers, although still more likely to associate Luxury and Status with the car, are more likely than users of other modes to associate these affects to active travel, perhaps due to an awareness of the benefits of walking and using the bicycle. Furthermore, high-income users of cars are more likely to experience consonance with respect to status and luxury, in what might be a form of self-congratulatory confirmation of success.

@@

In  this respect, it is important to note that the perception of users has been considered mainly from the lens of trip satisfaction, but the more granular approach taken in this study offers some advantages. For example, understanding dissonances reveals that public transport users are clearly at a disadvantage (i.e., they experience dissonance more frequently) compared to other travelers. Furthermore, the results reveal that within public transport users, there are also important socio-economic differences. In contrast, users of cars do not necessarily associate hedonic/eudaimonic values to this mode, which suggests that not only these feelings could be levaraged to attract them to active modes, but could also as a result lead to gains in wellbeing.

>>>>

The literature on SWB has demonstrated a relationship between people’s perceptions and satisfaction with their daily travel [e.g., @Smith2017commute; @Stlouis2014happy; @Mokhtarian2018travel]. Scholars have shown that accessibility is among the most studied factors that influences subjective wellbeing [@Delbosc2012role], and activities have a direct impact on travel satisfaction [@Bergstad2011subjective]. Delbosc [-@Delbosc2012role, p. 28], for instance, has summarized the most significant influences on psychological wellbeing: poverty and employment, meaningful relationships and health. However, understanding the components that affect these perceptions implies the differentiation between affective (also named as symbolic-affective) and instrumental values [@Bergstad2011affective]. Steg et al. (2011) have compared symbolic-affective and instrumental-reasoned motives for car-use, and similar findings are reported in other studies [e.g., @Gatersleben2007affective; @Lois2009relationship]. Previous research also demonstrates how socio-demographic factors affect the levels of SWB, including income [@Clark1996satisfaction; @Ferrer2005income], education and unemployment [@Argyle1999causes], age [@Diener1997subjective], and gender [@Tesch2008gender]. However, further research beyond the determinants of trip satisfaction is needed to understand how these socio-demographic variables connect with the affective reactions to various modes of travel [@Stlouis2014happy].

@@

The case study for the present research is Santiago. Santiago is the capital of Chile, a country with one of the highest levels of socio-economic inequality in the world. A tangible manifestation of the inequalities experienced by many in Chile is the large disparity in the relative cost of transportation, travel time, and distance traveled by different socio-economic segments of the population. To further complicate matters, strong spatial segregation also conditions car ownership and the use of public transportation – the higher the income, the higher the use of the automobile; conversely, the lower the income, the higher the reliance on public transportation. Although the transportation experience is but one of many dimensions of inequality, the experiences in this sector have triggered exceptional discomfort and dissatisfaction among the public. Recent social unrest, triggered by a seemingly minor hike in the fare of public transportation, brought many of these concerns to the forefront of the public conscience in dramatic fashion [e.g., @Davis2019].

@@

The study is based on a survey conducted in the city of Santiago during the months of November and December of 2016, at the end of the Spring and beginning of Summer seasons. The survey collected information on a wide range of transportation and related issues, and the data collection protocol considered a quota-sampling method for gathering the information, considering the socio-demographic information from Pre-Census of 2012. The survey was carried out face-to-face in centers of activity with dense provision of offices, services, and educational centers. An equal representation of both genders and a representation of the proportion of inhabitants per area were chosen as relevant characteristics of the sample. In total, there were $n=451$ valid responses, although not every response was complete and some questions have missing values.

The study considers data from 3 out of 8 sections of a longer survey. The relevant sections of the survey concern the individual characteristics of respondents, their feelings and affective responses related to their commute, and aspects describing their regular commute trips. In terms of individual characteristics and their commute, participants were asked socio-demographic information, including age (coded in three classes: younger than 35, older than 35 but younger than 55, and 55 and older); level of education (three classes: Kindergarten to grade 12, or K-12, technical diploma or university graduate, and graduate degree), income (three classes, by tertile), and the typical duration of the respondent's regular commute (four classes, by duration in minutes). The descriptive statistics of the sample appear in Figure \ref{fig:descriptive-statistics}. The sample trends to younger (56% is younger than 34 years old) and well-educated respondents (68% of respondents having technical or professional education), with an almost uniform distribution of income levels. The trend in typical commute time is towards longer commutes – e.g. 55% of the trips are longer than 40 minutes, and from those 56% corresponds to trips over the 60 minutes long.

@@

The next individual attribute that we examine is income, and in this case we detect significant differences in dissonance for three affective values: Poverty, Luxury, and Status. Poverty is a negative affect, and can be associated with the lack of a car [@Reutter2009who]. In our case, we see that lower income individuals tend to associate this feeling to their primary mode of commuting with higher frequency (almost 20% of the time) than other income groups. Whereas approximately 16% of mid-income people are dissatisfied with their primary mode of travel when it comes to evoking feelings of Poverty, less than 7% of high income individuals are. Dissonance with respect to Luxury and Status also tends to be more common among lower income individuals, and declines substantially for mid- and high income respondents. Notice as well that the frequency of dissonance is higher in terms of Luxury than Status for mid- and high income people.

@@

The preceding analysis indicates that there is significant mode dissonance along various dimensions and for various affective values. This is for the most part in line with previous research, although by examining different affective values individually instead of a summary measure of wellbeing, we are able to differentiate better the affective reactions of travelers. Less is known about the values that travelers associate with modes _other_ than the one they use. For this reason, after developing a profile of the travelers who experience mode dissonance in the preceding section, we are now interested in the responses of travelers with respect to the modes they ideally tend to associate with various affective values. 
For this analysis we employ a visualization technique known as _faceting_. Bar charts are used to plot the proportions of respondents who associate each mode of transportation with an affective value. Faceting allows us to explore these proportions in a multivariate way by slicing the data according to additional attributes. The result is a visual representation of a multi-way contingency table. Please note that due to the small numbers of travelers who use modes categorized as "Other" we henceforth exclude them from the analysis.

@@

Active travelers rarely experience dissonance with respect to Freedom, Enjoyment, and Happiness. And although the experience of dissonance is more frequent with respect to Luxury and Status, there is still a sizable plurality of active travelers who associate these two affective values with active travel, _not_ the car (contrast these to the responses of public transit users.)

@@

Interestingly, despite lower income individuals experiencing dissonance more frequently with respect to feelings of Poverty, we do not find that those feelings are specific to a transportation mode. In contrast, we see again that Luxury and Status generally are almost always attributed to the car, but with some interesting differences by income and primary mode of travel. Indeed, higher income active travelers, although still more likely to associate Luxury and Status with the car, are more likely than users of other modes to associate these affects to active travel, perhaps due to an awareness of the benefits of walking and using the bicycle. Furthermore, high-income users of cars are more likely to experience consonance with respect to status and luxury, in what might be a form of self-congratulatory confirmation of success.

@@

In  this respect, it is important to note that the perception of users has been considered mainly from the lens of trip satisfaction, but the more granular approach taken in this study offers some advantages. For example, understanding dissonances reveals that public transport users are clearly at a disadvantage (i.e., they experience dissonance more frequently) compared to other travelers. Furthermore, the results reveal that within public transport users, there are also important socio-economic differences. In contrast, users of cars do not necessarily associate hedonic/eudaimonic values to this mode, which suggests that not only these feelings could be leveraged to attract them to active modes, but could also as a result lead to gains in wellbeing.

### 2020-08-17 Dissonance_Santiago_v2/Dissonance_Santiago_v2.tex
v2 Revisions with BML

The literature on SWB has demonstrated a relationship between people's
perceptions and satisfaction with their daily travel (e.g., Smith, 2017;
Mokhtarian and Pendyala, 2018; St-Louis et al., 2014). Scholars have
shown that accessibility is among the most studied factors that
influences subjective wellbeing (Delbosc, 2012), and activities have a
direct impact on travel satisfaction (Cecilia Jakobsson Bergstad et al.,
2011). Delbosc (2012, p. 28), for instance, has summarized the most
significant influences on psychological wellbeing: poverty and
employment, meaningful relationships and health. However, understanding
the components that affect these perceptions implies the differentiation
between affective (also named as symbolic-affective) and instrumental
values (C. J. Bergstad et al., 2011). Steg et al.~(2011) have compared
symbolic-affective and instrumental-reasoned motives for car-use, and
similar findings are reported in other studies (e.g., Gatersleben and
Uzzell, 2007; Lois and Lopez-Saez, 2009). Previous research also
demonstrates how socio-demographic factors affect the levels of SWB,
includin income (Clark and Oswald, 1996; Ferrer-i-Carbonell, 2005),
education and unemployment (Argyle et al., 1999), age (Diener and
Eunkook Suh, 1997), and gender (Tesch-Römer et al., 2008). However,
further research beyond the determinants of trip satisfaction is needed
to understand how these socio-demographic variables connect with the
affective reactions to various modes of travel (St-Louis et al., 2014).

@@

The case study for the present research is Santiago. Santiago is the
capital of Chile, a country with one of the highest levels of
socio-economic inequality in the world. A tangible manifestation of the
inequalities experienced by many in Chile is the large disparity in the
relative cost of transportation, travel time, and distance traveled by
different socio-economic segments of the population. To further
complicate matters, strong spatial segregation also conditions car
ownership and the use of public transportation -- the higher the income,
the higher the use of the automobile; conversely, the lower the income,
the higher the reliance on public transportation. Although the
transportation experience is but one of many dimensions of inequality,
the experiences in this sector have triggered exceptional discomfort and
dissatisfaction among the public. Recent social unrest, triggered by a
seemingly minor hike in the fare of public transportation, has brought
many of these concerns to the forefront of the public conscience in
dramatic fashion (e.g., Davies, 2019; {\textbf{???}}; {\textbf{???}}).

Previous research has helped to contextualize everyday mobility in
Santiago relative to other Latin American cities (e.g., Avellaneda and
Lazo, 2011; Rodríguez Vignoli, 2008), but much remains to be explored.
Measuring instruments and new methods have led to more accurate and
precise understandings of the social issues that arise as consequence of
transport infrastructure and housing provision (Cox and Hurtubia, 2016),
and the minimum provision of basic services (Tiznado-Aitken et al.,
2016). However, the focus on accessibility as a measure of inequalities
remains predominant ({\textbf{???}}; Martínez et al., 2018; Niehaus et
al., 2016; Rojas et al., 2016).

@@

The study is based on a survey conducted in the city of Santiago during
the months of November and December of 2016, at the end of the Spring
and beginning of Summer seasons. The survey collected information on a
wide range of transportation and related issues, and the data collection
protocol considered a quota-sampling method for gathering the
information, considering the socio-demographic information from
Pre-Census of 2012. The survey was carried out face-to-face in centers
of activity with dense provision of offices, services, and educational
centers. An equal representation of both genders and a representation of
the proportion of inhabitants per area were chosen as relevant
characteristics of the sample. In total, there were \(n=451\) valid
reponses, although not every response was complete and some questions
have missing values.

The study considers data from 3 out of 8 sections of a longer survey.
The relevant sections of the survey concern the individual
characteristics of respondents, their feelings and affective responses
related to their commute, and aspects describing their regular commute
trips. In terms of individual characteristics and their commute,
participants were asked socio-demographic information, including age
(coded in three classes: younger than 35, older than 35 but younger than
55, and 55 and olde); level of education (three classes: Kindergarden to
grade 12, or K-12, technical diploma or university graduate, and
graduate degree), income (three classes, by tertile), and the typical
duration of the respondent's regular commute (four classes, by duration
in minutes). The descriptive statistics of the sample appear in Figure
\ref{fig:descriptive-statistics}. The sample trends to younger (56\% is
younger than 34 years old) and well-educated respondents (68\% of
respondents having technical or professional education), with an almost
uniform distribution of income levels. The trend in typical commute time
is towards longer commutes -- e.g.~55\% of the trips are longer than 40
minutes, and from those 56\% corresponds to trips over the 60 minutes
long.

@@

The next individual attribute that we examine is income, and in this
case we detect significant differences in dissonance for three affective
values: Poverty, Luxury, and Status. Since Poverty is a negative affect,
we see here that lower income individuals tend to associate this feeling
to their primary mode of commuting with higher frequency (almost 20\% of
the time) than other income groups. Whereas approximately 16\% of
mid-income people are dissatisfied with their primary mode of travel
when it comes to evoking feelings of Poverty, less than 7\% of high
income individuals are. Dissonance with respect to Luxury and Status
also tends to be more common among lower income individuals, and
declines substantially for mid- and high income respondents. Notice as
well that the frequency of dissonance is higher in terms of Luxury than
Status for mid- and high income people.

@@

The preceding analysis indicates that there is significant mode
dissonance along various dimensions and for various affective values.
This is for the most part in line with previous research, although by
examining different affective values individually instead of a summary
measure of wellbeing, we are able to differentiate better the affective
reactions of travelers. Less is known about the values that travelers
associate with modes \emph{other} than the one they use. For this
reason, after developing a profile of the travelers who experience mode
dissonance in the preceding section, we are now interested in the
responses of travelers with respect to the modes they ideally tend to
associate with various affective values. For this analysis we employ a
visualization technique known as \emph{faceting}. Bar charts are used to
plot the proportions of respondents who associate each mode of
transportation with an affective value. Faceting allows us to explore
these proportions in a multivariate way by slicing the data according to
additional attributes. The result is a visual representation of a
multi-way contingency table. Please note that due to the small numbers
of travellers who use modes categorized as ``Other'' we henceforth
exclude them from the analysis.

@@

Active travelers rarely experience dissonance with respect to Freedom,
Enjoyment, and Happiness. And although the experience of dissonance is
more frequent with respect to Luxury and Status, there is still a
sizeable plurality of active travellers who associate these two
affective values with active travel, \emph{not} the car (contrast these
to the responses of public transit users.)

@@

>>>>

The literature on SWB has demonstrated a relationship between people's
perceptions and satisfaction with their daily travel (e.g., Smith, 2017;
Mokhtarian and Pendyala, 2018; St-Louis et al., 2014). Scholars have
shown that accessibility is among the most studied factors that
influences subjective wellbeing (Delbosc, 2012), and activities have a
direct impact on travel satisfaction (Cecilia Jakobsson Bergstad et al.,
2011). Delbosc (2012, p. 28), for instance, has summarized the most
significant influences on psychological wellbeing: poverty and
employment, meaningful relationships and health. However, understanding
the components that affect these perceptions implies the differentiation
between affective (also named as symbolic-affective) and instrumental
values (C. J. Bergstad et al., 2011). Steg et al.~(2011) have compared
symbolic-affective and instrumental-reasoned motives for car-use, and
similar findings are reported in other studies (e.g., Gatersleben and
Uzzell, 2007; Lois and Lopez-Saez, 2009). Previous research also
demonstrates how socio-demographic factors affect the levels of SWB,
including income (Clark and Oswald, 1996; Ferrer-i-Carbonell, 2005),
education and unemployment (Argyle et al., 1999), age (Diener and
Eunkook Suh, 1997), and gender (Tesch-Römer et al., 2008). However,
further research beyond the determinants of trip satisfaction is needed
to understand how these socio-demographic variables connect with the
affective reactions to various modes of travel (St-Louis et al., 2014).

@@

The case study for the present research is Santiago. Santiago is the
capital of Chile, a country with one of the highest levels of
socio-economic inequality in the world. A tangible manifestation of the
inequalities experienced by many in Chile is the large disparity in the
relative cost of transportation, travel time, and distance traveled by
different socio-economic segments of the population. To further
complicate matters, strong spatial segregation also conditions car
ownership and the use of public transportation -- the higher the income,
the higher the use of the automobile; conversely, the lower the income,
the higher the reliance on public transportation. Although the
transportation experience is but one of many dimensions of inequality,
the experiences in this sector have triggered exceptional discomfort and
dissatisfaction among the public. Recent social unrest, triggered by a
seemingly minor hike in the fare of public transportation, brought many
of these concerns to the forefront of the public conscience in dramatic
fashion (e.g., Davies, 2019).

Previous research has helped to contextualize everyday mobility in
Santiago relative to other Latin American cities (e.g., Avellaneda and
Lazo, 2011; Rodríguez Vignoli, 2008), but much remains to be explored.
Measuring instruments and new methods have led to more accurate and
precise understandings of the social issues that arise as consequence of
transport infrastructure and housing provision (Cox and Hurtubia, 2016),
and the minimum provision of basic services (Tiznado-Aitken et al.,
2016). However, the focus on accessibility as a measure of inequalities
remains predominant (Martínez et al., 2018; Niehaus et al., 2016; Rojas
et al., 2016; Tiznado-Aitken et al., 2016).

@@

The study is based on a survey conducted in the city of Santiago during
the months of November and December of 2016, at the end of the Spring
and beginning of Summer seasons. The survey collected information on a
wide range of transportation and related issues, and the data collection
protocol considered a quota-sampling method for gathering the
information, considering the socio-demographic information from
Pre-Census of 2012. The survey was carried out face-to-face in centers
of activity with dense provision of offices, services, and educational
centers. An equal representation of both genders and a representation of
the proportion of inhabitants per area were chosen as relevant
characteristics of the sample. In total, there were \(n=451\) valid
responses, although not every response was complete and some questions
have missing values.

The study considers data from 3 out of 8 sections of a longer survey.
The relevant sections of the survey concern the individual
characteristics of respondents, their feelings and affective responses
related to their commute, and aspects describing their regular commute
trips. In terms of individual characteristics and their commute,
participants were asked socio-demographic information, including age
(coded in three classes: younger than 35, older than 35 but younger than
55, and 55 and older); level of education (three classes: Kindergarten
to grade 12, or K-12, technical diploma or university graduate, and
graduate degree), income (three classes, by tertile), and the typical
duration of the respondent's regular commute (four classes, by duration
in minutes). The descriptive statistics of the sample appear in Figure
\ref{fig:descriptive-statistics}. The sample trends to younger (56\% is
younger than 34 years old) and well-educated respondents (68\% of
respondents having technical or professional education), with an almost
uniform distribution of income levels. The trend in typical commute time
is towards longer commutes -- e.g.~55\% of the trips are longer than 40
minutes, and from those 56\% corresponds to trips over the 60 minutes
long.

@@

The next individual attribute that we examine is income, and in this
case we detect significant differences in dissonance for three affective
values: Poverty, Luxury, and Status. Poverty is a negative affect, and
can be associated with the lack of a car (Reutter et al., 2009). In our
case, we see that lower income individuals tend to associate this
feeling to their primary mode of commuting with higher frequency (almost
20\% of the time) than other income groups. Whereas approximately 16\%
of mid-income people are dissatisfied with their primary mode of travel
when it comes to evoking feelings of Poverty, less than 7\% of high
income individuals are. Dissonance with respect to Luxury and Status
also tends to be more common among lower income individuals, and
declines substantially for mid- and high income respondents. Notice as
well that the frequency of dissonance is higher in terms of Luxury than
Status for mid- and high income people.

@@

The preceding analysis indicates that there is significant mode
dissonance along various dimensions and for various affective values.
This is for the most part in line with previous research, although by
examining different affective values individually instead of a summary
measure of wellbeing, we are able to differentiate better the affective
reactions of travelers. Less is known about the values that travelers
associate with modes \emph{other} than the one they use. For this
reason, after developing a profile of the travelers who experience mode
dissonance in the preceding section, we are now interested in the
responses of travelers with respect to the modes they ideally tend to
associate with various affective values. For this analysis we employ a
visualization technique known as \emph{faceting}. Bar charts are used to
plot the proportions of respondents who associate each mode of
transportation with an affective value. Faceting allows us to explore
these proportions in a multivariate way by slicing the data according to
additional attributes. The result is a visual representation of a
multi-way contingency table. Please note that due to the small numbers
of travelers who use modes categorized as ``Other'' we henceforth
exclude them from the analysis.

@@

Active travelers rarely experience dissonance with respect to Freedom,
Enjoyment, and Happiness. And although the experience of dissonance is
more frequent with respect to Luxury and Status, there is still a
sizable plurality of active travelers who associate these two affective
values with active travel, \emph{not} the car (contrast these to the
responses of public transit users.)

@@

\leavevmode\hypertarget{ref-Reutter2009who}{}%
Reutter, L.I., Stewart, M.J., Veenstra, G., Love, R., Raphael, D.,
Makwarimba, E., 2009. ``Who do they think we are, anyway?'': Perceptions
of and responses to poverty stigma. Qualitative Health Research 19,
297--311.
doi:\href{https://doi.org/10.1177/1049732308330246}{10.1177/1049732308330246}
